Numerical simulation of the Cordilleran ice sheet through the last glacial cycle

### 2014-06-17 cordillera-cycle.tex
Add EPICA run deglaciation snapshots.

% fig:deglacshots
\begin{figure*}
  \includegraphics{deglacshots}
  \caption{Snapshots of modelled surface topography (200\,m contours)
           and surface velocity (colour mapping) from the GRIP simulation,
           corresponding to the last glacial maximum (-19.5 kyr) and the last
           deglaciation.
           \note{should we have a similar figure using EPICA?}}
  \label{fig:deglacshots}
\end{figure*}

>>>>

% fig:deglacshots-grip
\begin{figure*}
  \includegraphics{deglacshots-grip}
  \caption{Snapshots of modelled surface topography (200\,m contours)
           and surface velocity (colour mapping) from the GRIP simulation,
           corresponding to the last glacial ice volume maximum (-19.1 kyr) and
           the last deglaciation.}
  \label{fig:deglacshots-grip}
\end{figure*}

% fig:deglacshots-epica
\begin{figure*}
  \includegraphics{deglacshots-epica}
  \caption{Snapshots of modelled surface topography (200\,m contours)
           and surface velocity (colour mapping) from the EPICA simulation,
           corresponding to the last glacial ice volume maximum (-17.3 kyr) and
           the last deglaciation.}
  \label{fig:deglacshots-epica}
\end{figure*}
